### 2023-04-18 chapter2/chapter2.tex
Added references to supplement figures

The AICs were calculated for the models of each feature using their maximized likelihoods and two and three parameters for the BM and OU models, respectively. The pairwise differences in the AICs yielded a vector with 82 components, each representing the relative goodness of fit of the OU model over the BM model after accounting for their difference in complexity. The vectors were clustered using the correlation distance metric and the UPGMA algorithm. Clusters were manually chosen for subsequent GO analyses. To enrich these clusters for regions with a high likelihood of feature conservation despite high levels of sequence divergence, this analysis was restricted to regions whose amino acid and indel substitution rates exceeded 1 and 0.1, respectively.

\subsection{GO term analyses}
The 2022-03-22 go-basic release of the Gene Ontology was obtained from the GO Consortium website. The gene association file for the 2022\_02 release of the \textit{D. melanogaster} genome annotation was obtained from FlyBase. Obsolete annotations were dropped, and the remaining annotations were filtered by qualifiers and evidence code. The allowed qualifiers were ``enables,'' ``contributes\_to,'' ``involved\_in,'' ``located\_in,'' ``part\_of,'' and ``is\_active\_in.'' The allowed evidence codes were all experimental sources, traceable author statement (TAS), and inferred by curator (IC). The annotations were propagated up the ontology graph and joined with the region sets, so every annotation associated with a gene was associated with the regions derived from that gene. $P$-values were calculated with exact hypergeometric probabilities with regions considered as the sampling unit. For the disorder score analysis, the reference set was the filtered regions, and the enrichment set was regions in the upper decile of the score rate distribution. For the cluster analysis, the reference set was the filtered regions after the additional filtering by substitution rates, and the enrichments sets were the regions in each cluster.

>>>>

The AICs were calculated for the models of each feature using their maximized likelihoods and two and three parameters for the BM and OU models, respectively. The pairwise differences in the AICs yielded a vector with 82 components, each representing the relative goodness of fit of the OU model over the BM model after accounting for their difference in complexity. The vectors were clustered using the correlation distance metric and the UPGMA algorithm. Clusters were manually chosen for subsequent GO analyses. To enrich these clusters for regions with a high likelihood of feature conservation despite high levels of sequence divergence, this analysis was restricted to regions whose amino acid and indel substitution rates exceeded 1 and 0.1, respectively (Fig.~\ref{sfig:hierarchy_histogram}).

\subsection{GO term analyses}
The 2022-03-22 go-basic release of the Gene Ontology was obtained from the GO Consortium website. The gene association file for the 2022\_02 release of the \textit{D. melanogaster} genome annotation was obtained from FlyBase. Obsolete annotations were dropped, and the remaining annotations were filtered by qualifiers and evidence code. The allowed qualifiers were ``enables,'' ``contributes\_to,'' ``involved\_in,'' ``located\_in,'' ``part\_of,'' and ``is\_active\_in.'' The allowed evidence codes were all experimental sources, traceable author statement (TAS), and inferred by curator (IC). The annotations were propagated up the ontology graph and joined with the region sets, so every annotation associated with a gene was associated with the regions derived from that gene. $P$-values were calculated with exact hypergeometric probabilities with regions considered as the sampling unit. For the disorder score analysis, the reference set was the filtered regions, and the enrichment set was regions in the upper decile of the score rate distribution (Fig.~\ref{sfig:scores_histogram}). For the cluster analysis, the reference set was the filtered regions after the additional filtering by substitution rates, and the enrichments sets were the regions in each cluster.
